\renewcommand{\theFancyVerbLine}{%
{\small
ms.\arabic{FancyVerbLine}}}
 
\begin{Verbatim}[numbers=left]
ident = letter {letter | digit}.

number = integer | real.

integer = digit {digit} | octalDigit {octalDigit} ("B"|"C") |
          digit {hexDigit} "H".
          
real = digit {digit} "." {digit} {ScaleFactor}.

ScaleFactor = "E" ["+"|"-"] digit {digit}.

hexDigit = digit | "A" | "B" | "C" | "D" | "E" | "F".

digit = octalDigit | "8" | "9".

octalDigit = "0" | "1" | "2" | "3" | "4" | "5" | "6" | "7".

string = "'" {character} "'" | '"' {character} '"' .

qualident = ident {"." ident}.

ConstantDeclaration = ident "=" ConstExpression.

ConstExpression = expression.

TypeDeclaration = ident "=" type.

type = SimpleType | ArrayType | RecordType | SetType |
       PointerType | ProcedureType.
       
SimpleType = qualident | enumeration | SubrangeType.

enumeration = "(" IdentList ")".

IdentList = ident {"," ident}.

SubrangeType = [ident] "[" ConstExpression ".." ConstExpression "]".

ArrayType = ARRAY SimpleType {"," SimpleType} OF type.

RecordType = RECORD FieldListSequence END.

FieldListSequence = FieldList {";" FieldList}.

FieldList = [IdentList ":" type |
            CASE [ident] ":" qualident OF variant {"|" variant}
            [ELSE FieldListSequence] END].
            
variant = [CaseLabelList ":" FieldListSequence].

CaseLabelList = CaseLabels {"," CaseLabels}.

CaseLabels = ConstExpression [".." ConstExpression].

SetType = SET OF SimpleType.

PointerType = POINTER TO type.

ProcedureType = PROCEDURE [FormalTypeList].

FormalTypeList = "(" [ [VAR] FormalType
                 {"," [VAR] FormalType} ] ")" [":" qualident].
                 
VariableDeclaration = IdentList ":" type.

designator = qualident {"." ident | "[" ExpList "]" | "^"}.

ExpList = expression {"," expression}.

expression = SimpleExpression [relation SimpleExpression].

relation = "=" | "#" | "<" |"<=" | ">" | ">=" | IN.

SimpleExpression = ["+"|"-"] term {AddOperator term}.

AddOperator = "+" | "-" | OR.

term = factor {MulOperator factor}.

MulOperator = "*" |"/" | DIV | MOD | AND.

factor = number | string | set | designator [ActualParameters] |
        "(" expression ")" | NOT factor.
        
set = [qualident] "{" [element {"," element}] "}".

element = expression [".." expression].

ActualParameters = "(" [ExpList] ")" .

statement = [assignment | ProcedureCall |
            IfStatement | CaseStatement | WhileStatement |
            RepeatStatement | LoopStatement | ForStatement |
            WithStatement | EXIT | RETURN [expression] ].
            
assignment = designator ":=" expression.

ProcedureCall = designator [ActualParameters].

StatementSequence = statement {";" statement}.

IfStatement = IF expression THEN StatementSequence
              {ELSIF expression THEN StatementSequence}
              [ELSE StatementSequence] END.
              
CaseStatement = CASE expression OF case {"|" case}
                [ELSE StatementSequence] END.
                
case = [CaseLabelList ":" StatementSequence].

WhileStatement = WHILE expression DO StatementSequence END.

RepeatStatement = REPEAT StatementSequence UNTIL expression.

ForStatement = FOR ident ":=" expression TO expression
               [BY ConstExpression] DO StatementSequence END.
               
LoopStatement = LOOP StatementSequence END.

WithStatement = WITH designator DO StatementSequence END .

ProcedureDeclaration = ProcedureHeading ";" block ident.

ProcedureHeading = PROCEDURE ident [FormalParameters].

block = {declaration} [BEGIN StatementSequence] END.

declaration = CONST {ConstantDeclaration ";"} |
              TYPE {TypeDeclaration ";"} |
              VAR {VariableDeclaration ";"} |
              ProcedureDeclaration ";" | ModuleDeclaration ";".
              
FormalParameters = "(" [FPSection {";" FPSection}] ")" [":" qualident].

FPSection = [VAR] IdentList ":" FormalType.

FormalType = [ARRAY OF] qualident.

ModuleDeclaration = MODULE ident [priority] ";" [import] [export] block ident.

priority = "[" ConstExpression "]".

export = EXPORT [QUALIFIED] IdentList ";".

import = [FROM ident] IMPORT IdentList ";".

DefinitionModule = DEFINITION MODULE ident ";"

                   {import} {definition} END ident "." .
                   
definition = CONST {ConstantDeclaration ";"} |
             TYPE {ident ["=" type] ";"} |
             VAR {VariableDeclaration ";"} |
             ProcedureHeading ";".
             
ProgramModule = MODULE ident [priority] ";" {import} block ident ".".

CompilationUnit = DefinitionModule | [IMPLEMENTATION] ProgramModule.
\end{Verbatim}



